<!-- The experiment was conducted from July 2014 to November 2014.  -->
<!--  Message was three times: at the launch of the submission phase, eight days from the launch and two days before the end of the submission phase of the challenge. -->

# Experimental Design
## The context

The Heart Center is a leading academic medical center specializing in clinical cardiac care and research in the United States. Founded more than a hundred years ago, the Heart Center serves thousands of patients every year, occupies more than 35,000 square feet of office space, and employs more than 1,200 people (nurses, physicians, researchers, technicians, and administrative staff) scattered across several buildings on the Massachusetts General Hospital's main campus in downtown Boston and a few other satellite locations.

The study was in cooperation with the Heart Center's launch of the Healthcare Transformation Lab (HTL),^[http://www.healthcaretransformation.org] an initiative aimed at developing innovative health care process improvements to enhance the health care safety and delivery of the hospital. The launch of the HTL was accompanied by the announcement of an internal "innovation contest," called the Ether Dome Challenge^[The name is taken from a historical place on MGH's main campus where the first public surgery using anesthesia was demonstrated in 1846.] that sought to engage all staff members to participate. 

The communication around the innovation contest highlighted the opportunity for staff to help in the selection process of the ideas and a commitment by the Heart Center Management that the leading ideas would be provided appropriate resources so that they could be implemented. The announcement on the contest's website read:

> "If you've noticed something about patient experience, employee satisfaction, workplace efficiency, or anything that could be improved; if you've had an inspiration about a new way to safeguard health; or if you simply have a cost-saving idea, then now is the time to share your idea."

```{r methods_timeline, fig.width=9, fig.height=5, include=FALSE}
```

\begin{figure}
\centering
\caption{Timeline of the innovation contest}
\label{timeline}
\includegraphics{figures/methods_timeline-1.pdf}
\end{figure}


The innovation contest was divided into three main phases (Figure \ref{timeline}): submission, the peer evaluation, and implementation phase.

The first was a four-week submission phase. All staff members were encouraged to identify one or more organizational problems and submit proposals addressing them. Employee participation was voluntary. All project submissions were done online via the website of the contest. There was no limit to the project proposals to submit (proposals could cover any issue within the organization, as described above), but each proposal was limited to approximately 300 words to lower the costs of entry and encourage broader participation. To ensure that treatment effects could be isolated, identified, and matched to participants, team submissions were not permitted. Limiting submissions to individual participation allowed us to match each submitter's characteristics to the randomly assigned treatment. It also lowered incentives to communicate or exchange information with other employees. Also, the website was designed to not provide any information about the status of the contest during the submission period. In this way, decisions could not be easily influenced by the perceived popularity of the contest or previous submissions.

It followed a two-week peer evaluation phase in which all staff members were invited to rate the merit and potential of submitted proposals on a five-point rating scale. All evaluations were done online on the website of the contest. Each signed-up employee was shown a list of anonymized proposals to read and rate. Proposals were presented at random in batches of 10 each. Each proposal was described by a title, a main description of the problem to solve, and the proposal. Voting was then introduced by the following text: "Rate this idea" followed by the rating scale: 1-low; 2; 3; 4; 5-high. Ratings were kept confidential and the website did not provide any feedback or any other kind of additional information that might have influenced individual judgment until the voting phase was over. Evaluators were free to decide how many (and which) proposals to rate. Since these were presented in a random order, every proposal had on average the same exposure to people asked to rate its quality. Evaluators were offered a limited edition T-shirt as a compensation for the effort in voting.

In the final implementation phase, employees having submitted proposals highly rated by peers and judged as particularly promising by the HTL staff were invited to submit a full proposal detailing plans for implementation. Following evaluation by MGH senior leadership, top proposals were selected to receive support and funding for implementation. This final phase took a few months to complete, essentially the time necessary to select and implement the best projects.

## The design

Within this context, we designed a _natural field experiment_ (staff members are unaware of being part of an experiment). The basic idea of the experiment was to randomize the content of the communication announcing the innovation contest to all staff members. The start of the submission phase was indeed announced to everyone in a series of personalized emails. A direct message was sent to each contact in the list of employees' emails from our subject pool. 

The content of this communication with a placeholder for our solicitation treatment is reported below (a copy of the exact email is in the Appendix). 

> Dear Heart Center team member,
>    
> **Submit your ideas to [TREATMENT HERE]**
>    
> The Ether Dome Challenge is your chance to submit ideas on how to improve the MGH Corrigan Minehan Heart Center, patient care and satisfaction, workplace efficiency and cost. All Heart Center Staff are eligible to submit ideas online. We encourage you to submit as many ideas as you have: no ideas are too big or too small!
>
> Submissions will be reviewed and judged in two rounds, first by the Heart Center staff via crowd-voting, and then by an expert panel. Winning ideas will be eligible for project implementation funding in the Fall of 2014!

The first paragraph of the above message was randomized into _four_ different solicitation treatments (the exact words are in Table \ref{experimental-design}), thus creating as many treatment groups of equal size (Table \ref{experimental-design}). The first group was given a solicitation treatment (PRIZE) announcing the innovation contest as an opportunity to win individual prizes (iPad mini's) for top submissions. The second group was given a solicitation treatment (FUND) announcing the contest as an opportunity to  win a $20,000 budget for developing their project proposals. The other groups received solicitation treatments announcing the contest as an opportunity to improve the health care of their patients (PCARE) or the workplace (WPLACE).

```{r methods_experimental_design, results='asis'}
```

A sample size of more than 300 units for each treatment group ensured a sufficiently high statistical power based upon standard power calculations on the difference of proportions. In testing the difference of proportions between any two treatments, the probability of type-I errors was slightly below $0.80$ for _small_ differences at 5 percent significance level but higher than $0.80$ for _medium_ and _large_ differences at the more stringent 1 percent significance level.^[The definition of small, medium and large differences is given by @cohen1992power;  e.g., a difference of 5 percentage points of the pair $(0.05, 0.10)$ is considered a small effect: see @cohen1992power p. 158.]

Also, note the lack of a traditional "control" treatment in this study. Since the experiment was run in a workplace, we were constrained to carry out treatments having equal chances of being successful. This prevented us from having a 'null' treatment with no personalized incentives messaging as a control group. Indeed, the analysis focused on multiple comparisons of several unordered discrete treatments (e.g., prizes vs funding vs framing).^[Nevertheless, if we were to think of one treatment as the benchmark against which to compare the others, the FUND treatment would be our best candidate because giving information about the size of available funding is the default option for announcing grant programs and was part of the HTL's initial design before our cooperation in the experiment.]

These solicitation messages were sent three times: at the launch of the submission phase, eight days from the launch and two days before the end of the submission phase of the challenge.

The website of the innovation contest had supporting information about the available prizes, funding, and timing of the initiative. The website also required an institutional email address to login. Using this feature, we designed the website graphics and layout to reinforce the effect of the announcement: the headings, background images, a short video, and the space just below a "submit your ideas" button were designed to show the exact same first paragraph of the solicitation that the employee received by email (i.e., text in Table \ref{experimental-design}).

The MGH management and the HTL staff members were blind to group assignment, which prevented potential bias in the communication of the innovation contest that was not under our direct control. We also made an effort to create a "safe" environment for employees submitting proposals by making clear (in the application form) that the identity of the proponents was going to be kept private unless the employee self-identified, so that management could not identify workers without their consent.

Finally, we relied only on official channels for communication to strengthen the effect of the announcement and signal legitimacy of the contest. Each employee received the same exact solicitation email three times: at the launch, eight days from the launch and two days before the end of the submission phase of the challenge. Starting from the second week of the submission phase, information booths, flyers, and posters were used to encourage everyone to take part in the event and respond to the email solicitation. These flyers and posters were based on a generic, undifferentiated version of the solicitation email without the text of the treatments.


# Data

```{r}
pc_women    <- round(100*mean(hc$gender=='female'))
pc_nurses   <- round(100*mean(hc$job=='Nursing'))
pc_women_nurses <- round(100*mean(hc$gender[hc$job=='Nursing']=='female'))
n_survey    <- sum(hc$has_survey=='yes')
pc_survey   <- round(100*mean(hc$has_survey=='yes'))
```

Our subject pool is the entire population working at the Heart Center as of the end of 2014, a total of `r format(nrow(hc), big.mark=',')` individuals. For each individual, we have administrative data on the gender, the type of profession, and whether they had a fixed office location or not. Additional, complementary data are available for a limited group of `r n_survey` employees (`r pc_survey` percent). These extra data have self-reported information about employees' demographics, such as age and years of tenure at the Heart Center, that were obtained from an online survey that was run about two months before the launch of the innovation contest. 

We report summary statistics for the different variables by solicitation treatment (Table \ref{summary-statistics}), showing that these are statistically balanced across groups. These also show that the large majority (`r pc_women` percent) of employees in our sample are women. This is due to the high fraction of workers being nurses (`r pc_nurses` percent) and the presence of a gender separation by profession with nurses being predominantly women (`r pc_women_nurses` percent). 
 
Nursing workers constitute about half of the sample, and the rest is split almost equally between physicians and administrative workers. Though we do not have data on income, there exist large differences in earnings across these professions. According to the United States Bureau of Labor Statistics, the median annual wage of a physician was $187,200 in 2015, which is about 60 percent higher than the that of a registered nurse ($67,490) and about 70 percent higher than that of a laboratory technician ($38,970). It follows that, if staff members are motivated by the extrinsic value of the prize alone, one should expect large differences in participation rates across profession.

Finally, it is also important to remark that only half of the employees ($53$ percent) have fixed office locations, as they may be on duty in multiple wards. However, more senior staff tend to have a fixed location. So, within each profession, this measure can be viewed as a proxy for the employee's position or status inside the organization. 


```{r methods_summary_stats, results="asis"}
```

